Feeding Dynamic Behavior into Optimization: Simulation-based Multi-objective Overtime Planning

### 2014-08-29 data/result/Article/Latex/Article.tex
pequenos ajustes

To determine the most adequate stop criteria, we executed NSGAII for all selected instances with a maximum of 5,000, 10,000, 20,000, and 50,000 fitness evaluations. To properly account for the randomness inherent to heuristic search algorithms, the optimization was executed 50 times for each configuration and instance. Fifty thousand fitness evaluations was considered as an upper limit due to the time required to process each optimization cycle, particularly due to the cost of running the simulation on every fitness function evaluation. Afterwards, we built a reference front for each instance based on non-dominated solutions collected from all 50 cycles of all configurations under which the instance was optimized. Then, we calculated $I_{GD}$ for the front resulting from each optimization cycle based on the reference front. This led to a data frame containing 50 observations of $I_{GD}$ for each instance and configuration. Being bound to the [0..1] interval, quality indicators data cannot be normally-distributed and thus cannot be subjected to parametric statistical inference test. Thus, hereafter we will only use non-parametric tests. A Kruskal-Wallis non-parametric inference test was executed upon this data and found significant differences between configurations at 95\% significance level. A post-hoc analysis based on pair-wise comparisons through a Wilcoxon test using Bonferroni correction followed to find that there were significant differences among all configurations and the configuration using 50,000 fitness evaluations as stop criteria yielded smaller I$_{GD}$ for all instances. Thus, we used 50,000 fitness evaluations as stop criteria for all following analysis.

@@

% Table generated by Excel2LaTeX from sheet 'tabela 4'
\begin{table}[htbp]
	\scriptsize
  \centering
  \caption{Quality indicators for each instance under our approach (NSGAII) and a model without error dynamics (NSGA$_{NE}$). Pareto fronts for NSGA$_{NE}$ cover a larger part of the search space, leading to small $I_{GD}$. Solutions produced under NSGAII tend to concentrate in certain parts of the search space}
    \begin{tabular}{p{0.8cm}p{1.0cm}ccc}
    \toprule
    \textbf{Instance} & \textbf{Config.} & \textbf{I$_{C}$} & \textbf{I$_{HV}$} & \textbf{I$_{GD}$} \\
    \midrule
    \multirow{2}[2]{*}{ACAD} & NSGAII & 0.020 $\pm$ 0.022 & \textbf{0.464 $\pm$ 0.009} & 0.0066 $\pm$ 0.002 \\
          & NSGA$_{NE}$ & \textbf{0.020 $\pm$ 0.004} & 0.333 $\pm$ 0.001 & \textbf{0.0003 $\pm$ 0.0} \\\hline
    \multirow{2}[2]{*}{WMET} & NSGAII & 0.020 $\pm$ 0.019 & \textbf{0.492 $\pm$ 0.006} & 0.0037 $\pm$ 0.0 \\
          & NSGA$_{NE}$ & 0.020 $\pm$ 0.003 & 0.334 $\pm$ 0.001 & \textbf{0.0003 $\pm$ 0.0} \\\hline
    \multirow{2}[2]{*}{WAMS} & NSGAII & 0.020 $\pm$ 0.016 & \textbf{0.479 $\pm$ 0.004} & 0.0032 $\pm$ 0.0 \\
          & NSGA$_{NE}$ & 0.020 $\pm$ 0.003 & 0.337 $\pm$ 0.001 & \textbf{0.0002 $\pm$ 0.0} \\\hline
    \multirow{2}[2]{*}{PSOA} & NSGAII & 0.020 $\pm$ 0.014 & \textbf{0.421 $\pm$ 0.014} & 0.0129 $\pm$ 0.004 \\
          & NSGA$_{NE}$ & 0.020 $\pm$ 0.002 & 0.338 $\pm$ 0.001 & \textbf{0.0001 $\pm$ 0.0} \\\hline
    \multirow{2}[2]{*}{OMET} & NSGAII & 0.020 $\pm$ 0.014 & \textbf{0.465 $\pm$ 0.006} & 0.0044 $\pm$ 0.0 \\
          & NSGA$_{NE}$ & 0.020 $\pm$ 0.003 & 0.336 $\pm$ 0.001 & \textbf{0.0001 $\pm$ 0.0} \\\hline
    \multirow{2}[2]{*}{PARM} & NSGAII & 0.020 $\pm$ 0.019 & \textbf{0.489 $\pm$ 0.011} & 0.0090 $\pm$ 0.001 \\
          & NSGA$_{NE}$ & \textbf{0.020 $\pm$ 0.003} & 0.338 $\pm$ 0.001 & \textbf{0.0001 $\pm$ 0.0} \\
    \bottomrule
    \end{tabular}%
\end{table}%

>>>>

To determine the most adequate stop criteria, we executed NSGAII for all selected instances with a maximum of 5,000, 10,000, 20,000, and 50,000 fitness evaluations. To properly account for the randomness inherent to heuristic search algorithms, the optimization was executed 50 times for each configuration and instance. Fifty thousand fitness evaluations was considered as an upper limit due to the time required to process each optimization cycle, particularly due to the cost of running the simulation on every fitness function evaluation. Afterwards, we built a reference front for each instance based on non-dominated solutions collected from all 50 cycles of all configurations under which the instance was optimized. Then, we calculated $I_{GD}$ for the front resulting from each optimization cycle based on the reference front. This led to a data frame containing 50 observations of $I_{GD}$ for each instance and configuration. Being bound to the [0, 1] interval, quality indicators data cannot be normally-distributed and thus cannot be subjected to parametric statistical inference test. Thus, hereafter we will only use non-parametric tests. A Kruskal-Wallis non-parametric inference test was executed upon this data and found significant differences between configurations at 95\% significance level. A post-hoc analysis based on pair-wise comparisons through a Wilcoxon test using Bonferroni correction followed to find that there were significant differences among all configurations and the configuration using 50,000 fitness evaluations as stop criteria yielded smaller I$_{GD}$ for all instances. Thus, we used 50,000 fitness evaluations as stop criteria for all following analysis.

@@

% Table generated by Excel2LaTeX from sheet 'tabela 4'
\begin{table}[htbp]
	\scriptsize
  \centering
  \caption{Quality indicators for each instance under our approach (NSGAII) and a model without error dynamics (NSGA$_{NE}$). Pareto fronts for NSGA$_{NE}$ cover a larger part of the search space, leading to smaller $I_{GD}$. Solutions produced under NSGAII tend to concentrate in certain parts of the search space}
    \begin{tabular}{p{0.8cm}p{1.0cm}ccc}
    \toprule
    \textbf{Instance} & \textbf{Config.} & \textbf{I$_{C}$} & \textbf{I$_{HV}$} & \textbf{I$_{GD}$} \\
    \midrule
    \multirow{2}[2]{*}{ACAD} & NSGAII & 0.020 $\pm$ 0.022 & \textbf{0.464 $\pm$ 0.009} & 0.0066 $\pm$ 0.002 \\
          & NSGA$_{NE}$ & \textbf{0.020 $\pm$ 0.004} & 0.333 $\pm$ 0.001 & \textbf{0.0003 $\pm$ 0.0} \\\hline
    \multirow{2}[2]{*}{WMET} & NSGAII & 0.020 $\pm$ 0.019 & \textbf{0.492 $\pm$ 0.006} & 0.0037 $\pm$ 0.0 \\
          & NSGA$_{NE}$ & 0.020 $\pm$ 0.003 & 0.334 $\pm$ 0.001 & \textbf{0.0003 $\pm$ 0.0} \\\hline
    \multirow{2}[2]{*}{WAMS} & NSGAII & 0.020 $\pm$ 0.016 & \textbf{0.479 $\pm$ 0.004} & 0.0032 $\pm$ 0.0 \\
          & NSGA$_{NE}$ & 0.020 $\pm$ 0.003 & 0.337 $\pm$ 0.001 & \textbf{0.0002 $\pm$ 0.0} \\\hline
    \multirow{2}[2]{*}{PSOA} & NSGAII & 0.020 $\pm$ 0.014 & \textbf{0.421 $\pm$ 0.014} & 0.0129 $\pm$ 0.004 \\
          & NSGA$_{NE}$ & 0.020 $\pm$ 0.002 & 0.338 $\pm$ 0.001 & \textbf{0.0001 $\pm$ 0.0} \\\hline
    \multirow{2}[2]{*}{OMET} & NSGAII & 0.020 $\pm$ 0.014 & \textbf{0.465 $\pm$ 0.006} & 0.0044 $\pm$ 0.0 \\
          & NSGA$_{NE}$ & 0.020 $\pm$ 0.003 & 0.336 $\pm$ 0.001 & \textbf{0.0001 $\pm$ 0.0} \\\hline
    \multirow{2}[2]{*}{PARM} & NSGAII & 0.020 $\pm$ 0.019 & \textbf{0.489 $\pm$ 0.011} & 0.0090 $\pm$ 0.001 \\
          & NSGA$_{NE}$ & \textbf{0.020 $\pm$ 0.003} & 0.338 $\pm$ 0.001 & \textbf{0.0001 $\pm$ 0.0} \\
    \bottomrule
    \end{tabular}%
\end{table}%
